%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[normalem]{ulem}

\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{ifthen}

% Define a boolean variable
\newboolean{isRedacted}
\setboolean{isRedacted}{false} % Set this to true or false

% Define the redacted command
\newcommand{\redact}[1]{%
    \ifthenelse{\boolean{isRedacted}}{\sout{REDACTED}}{#1}%
}


% Test the redacted command

% You can change the value of the boolean variable to see the different outputs
%\setboolean{isRedacted}{false}
%\redacted{This is the actual value.}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape \redact{Mohammed Nasser}} \\ \vspace{1pt}
    \small \redact{+201207342864} $|$ \href{mailto:mohammednh2864@gmail.com}{\underline{\redact{mohammednh2864}@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/\redact{elweday}}} $|$
    \href{https://github.com/...}{\underline{github.com/\redact{elweday}}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading{\redact{Helwan} University}{\redact{Cairo, EG}}{Bachelor of Computer and Communication Engineering }{Oct 2021 -- Aug 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{Nov 2023 -- Present}
      {\redact{@studyo.io}}{Remote}
      \resumeItemListStart
        \resumeItem{Orchestrated the development of backend video processing containerized microservices on Google Cloud using golang and python, integrated CI/CD methodologies to enhance agility and efficiency, leading to a 50\% decrease in development cycles.}
        \resumeItem{Developed and documented CLI tools and modular solutions to automate repetitive development tasks, saving 20\% development time and boosting team productivity.}
        \resumeItem{Used advanced math to create visually compelling animations using LaTeX, ffmpeg, OpenGL, fostering immersive learning experiences and optimizing for performance for both rendering and response times.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Javascript, Typescript, Python, Golang, C, C++, Java, HTML, CSS} \\
     \textbf{Technical Skills}{: Git, Github, Linux, Docker, CI/CD, Design Patterns, ETL, Web Scraping, Software Testing. Scripting.} \\
     \textbf{Technologies}{:  React, Node.js, Express, Next.js, Django, Flask, Svelte} \\
     \textbf{Cloud (GCP)}{: iAM, Vertex, Run, Functions, Compute, Storage, Artifact Registry, Firestore.} \\ 
     \textbf{Data-Driven}{: SQL, NoSQL, ORMs, Database Management, REST, RPC, GraphQL, Event Driven APIs, Websockets.}

    }}
 \end{itemize}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{College Tracking System}}{}
          \resumeItemListStart
            \resumeItem{Designed and populated a Database PostgreSQL, for a college website for grade tracking}
            \resumeItem{Using SvelteKit Crafted interactive views for educators and students, with charts, timetables, grades, course tracking and registration for students \& prioritizing UX \& accessibility.}
            \resumeItem{Implemented A RESTful APIs to connect the frontend and the backend}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Scribble}}{}
          \resumeItemListStart
            \resumeItem{A game where you alternate between drawing and guessing the words that the other players drew, built using Next.js, React, YJS, Websockets, and TailwindCSS.}
            \resumeItem{The game is made real-time and collaborative using websockets for communication between peers and a custom state machine to manage game logic.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{Metropection}}{}
          \resumeItemListStart
            \resumeItem{n app for our local metro network, utilizing graph data structures and pathfinding algorithms to compute optimal routes. By scraping data from Google Maps, I ensured precise station locations and transit routes. The user-friendly interface offers real-time insights on travel duration and cost, improving the commuter experience.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


\section{Extracurricular Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Head of Data Science Committee }{Nov 2022 -- Oct 2023}
      {\redact{@Energia Powered}}{}
      \resumeItemListStart
        \resumeItem{Led a team of four to deliver impactful Data Science initiatives through biweekly workshops, crafting interactive learning materials such as presentations and Jupyter notebooks.}
        \resumeItem{Directed and collaborated with participants in workshop sessions focused on essential data science topics, including Python Programming, Exploratory Data Analysis (EDA), Machine Learning (ML), Deep Learning (DL), Statistical Methodologies, and Mathematics.}
        \resumeItem{Provided guidance and support to workshop participants throughout their final projects, fostering practical application of learned concepts.}
      \resumeItemListEnd
      

\end{document}
