%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[normalem]{ulem}

\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{ifthen}

% Define a boolean variable
\newboolean{isRedacted}
\setboolean{isRedacted}{false}

% Define the redacted command
\newcommand{\redact}[1]{%
    \ifthenelse{\boolean{isRedacted}}{\sout{REDACTED}}{#1}%
}


% Test the redacted command

% You can change the value of the boolean variable to see the different outputs
%\setboolean{isRedacted}{true}
%\redacted{This is the actual value.}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
	\textbf{\Huge \scshape \redact{Mohammed Nasser}} \\ \vspace{1pt}
	\small 
  \href{mailto:mohammednh2864@gmail.com}{\underline{\redact{mohammednh2864}@gmail.com}} $|$
	\href{https://linkedin.com/in/elweday}{\underline{linkedin.com/in/\redact{elweday}}} $|$
	\href{https://github.com/elweday}{\underline{github.com/\redact{elweday}}} $|$
  \href{https://elweday.vercel.app}{\redact{\underline{elweday.vercel.app}}} $|$
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{\redact{Studyo}}{London, UK }{Software Developer \small (Remote)}{Nov 2023 -- Present}
\resumeItemListStart
\resumeItem{Orchestrated the development of backend video processing containerized microservices on Google Cloud Platform using Go and Python to serve as a backend for a mobile applications and internal services.}
\resumeItem{Integrated CI/CD pipelines with GitHub Actions and Docker, cutting deployment times by 50\% and significantly reducing integration errors.}
\resumeItem{Developed and documented CLI tools and modular solutions to automate repetitive development tasks, saving the team 10 hours per week on average.}
\resumeItem{Created +30 complex animations with LaTeX, ffmpeg, and OpenGL, visualizing abstract concepts for the company's e-learning platform.}
\resumeItem{Collaborated with a team to create a website for the company, showcasing the company's products and services.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{\redact{Helwan} University}{\redact{Cairo, EG}}{Bachelor of Computer and Communication Engineering }{Oct 2021 -- Aug 2026} \\
\vspace{0.25cm}\small{\textbf{Relevant Coursework}{: Operating Systems, Object Oriented Programming, Data Structures and Algorithms, Databases, Computer Architecture, Microprocessors Microcontrollers, .}} \\
\resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Languages}{: JavaScript, TypeScript, Python, Go, C, C++, Java} \\
	      \textbf{Web}{:  HTML, CSS, React, Node.js, Express, Next.js, Django, Flask, Svelte.} \\
	      \textbf{Cloud \& DevOps}{: Docker, CI/CD, GCP(iAM, Vertex, Run, Functions, Compute, Storage, Firestore).} \\
	      \textbf{Data \& APIs}{: SQL, MongoDB, NoSQL, ORMs, Database, REST, gRPC, GraphQL, Websockets.} \\
	      \textbf{Other}{: Git, Github, Linux, Docker, CI/CD, Design Patterns, Web Scraping, Testing, Scripting, Microservices} \\
	      }}
\end{itemize}


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\href{https://github.com/elweday/scribble}{\underline{\textbf{Scribble}}}}{}

\resumeItemListStart
\resumeItem{Engineered a real-time multiplayer drawing and guessing game using Next.js, React, and WebSockets.}
\resumeItem{Leveraged YJS for synchronizing the drawing state between peers providing a conflict-free real-time collaboration, enabling seamless drawing experiences across devices.}
\resumeItem{Implemented a custom state machine to manage game logic, ensuring smooth and efficient gameplay.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/elweday/CollegeSite}{\underline{\textbf{College Management System}}}}{}
\resumeItemListStart
\resumeItem{Architected a comprehensive academic portal using SvelteKit and PostgreSQL, providing a robust platform for educators and students.}
\resumeItem{Designed an intuitive UI for course registration, grade tracking, and timetable management.}
\resumeItem{Integrated data visualization tools, providing insightful analytics on student performance and course popularity.}
\resumeItem{Developed and maintained a comprehensive backend API, ensuring seamless integration with the frontend.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/elweday/elweday.github.io-metro}{\underline{\textbf{Metropection}}}}{}
\resumeItemListStart
\resumeItem{Designed a responsive UI that handles complex map interactions smoothly on both desktop and mobile devices.}
\resumeItem{Created an efficient pathfinding algorithm, improving route calculation speed by 75\% compared to existing solutions.}
\resumeItem{Integrated real-time data from Google Maps API, achieving 98\% accuracy in travel time predictions.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\section{Extracurricular Activities}
\resumeSubHeadingListStart
\resumeSubheading{Energia Powered }{Cairo, EG}{Head of Data Science Committee}{Nov 2022 -- Oct 2023}
\resumeItemListStart
\resumeItem{Led a team of 4 to develop and deliver a comprehensive data science curriculum, training over 40 students.}
\resumeItem{Organized and facilitated 15+ workshops covering advanced topics in Data Science, Machine Learning and Deep Learning.}
\resumeItem{Mentored 20+ students in capstone projects, with 3 projects selected for presentation at a national tech conference.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
